### 2023-02-06 REV_Polak1/Polak1.tex
Final commit before sending to the editors for corrections

\begin{newrevengenv}{Paweł Polak}
	{Why is neuron modeling of particular philosophical interest?}
	{Why is neuron modeling of particular philosophical interest?}
	{Why is neuron modeling of particular philosophical interest?}
	{Pontifical University of John Paul II in Krakow}
	{Andrzej Bielecki, \textit{Models of Neurons and Perceptrons: Selected Problems and Challenges}, Springer International Publishing, Cham 2019, pp. 156; Studies in Computational Intelligence Volume vol. 770, DOI: \href{https://doi.org/10.1007/978-3-319-90140-4}{10.1007/978-3-319-90140-4}.}

@@

A~peculiarity of ``philosophy in science''
%\label{ref:RNDSoIfWpdNhG}(see Heller, 2019; Polak, 2019)
\parencites[see][]{heller_how_2019}[][]{polak_philosophy_2019} %
 is that the best sources tend to be atypical from the viewpoint of most philosophers: For example, on the one hand, there are works that popularize science, while on the other hand, there are research articles and even specialized monographs. The book discussed here falls into the last category, and it is devoted to modeling neurons and perceptrons. It was written by a~mathematician from Kraków, Andrzej Bielecki, who is currently working at the AGH University of Science and Technology.\footnote{Andrzej Bielecki received an M.Sc. degree in Physics and Mathematics and a~Ph.D. in Mathematics, D.Sc. (habilitation) in Mathematics from the Jagiellonian University in Kraków. He obtained a~professorship in Computer Science in 2020. His fields of interest includes dynamical systems theory, artificial intelligence, cybernetics, and philosophy of science, and he has written over 120 scientific papers and one textbook.} Readers of \textit{ZFN}, as well as the related \textit{Semina Scientiarum} journal, will probably associate him with the philosophical activities that he has practiced within the context of his scientific activities 
%\label{ref:RNDkz8F1S0BJI}(Bielecki, 2016; 2018).
\parencites*[][]{bielecki_cybernetyczna_2016}[][]{bielecki_epistemologiczne_2018}. %
 Bielecki is an example of a~scientist–philosopher from the Krakow milieu,\footnote{It is worth mentioning that in the book, Bielecki mostly uses examples from research conducted in the Kraków milieu. The use of the cybernetic theory framework could also be interpreted as another sign of the local milieu's influence.} and it is worth noting that he develops his philosophical activities, among other things, through his work on the Committee on Philosophy of Science at the Polish Academy of Arts and Sciences in Kraków.

>>>>

\begin{newrevengenv}{Paweł Polak}
	{Why is neuron modeling of particular philosophical interest?}
	{Why is neuron modeling of particular philosophical interest?}
	{Why is neuron modeling of particular philosophical interest?}
	{Pontifical University of John Paul II in Krakow}
	{Andrzej Bielecki, \textit{Models of Neurons and Perceptrons: Selected Problems and Challenges}, Studies in Computational Intelligence, vol. 770, Springer International Publishing, Cham 2019, pp. 156.}
%	; Studies in Computational Intelligence Volume vol. 770, DOI: \href{https://doi.org/10.1007/978-3-319-90140-4}{10.1007/978-3-319-90140-4}.}

@@

\lettrine[loversize=0.13,lines=2,lraise=-0.03,nindent=0em,findent=0.2pt]%
{A}{}peculiarity of ``philosophy in science''
%\label{ref:RNDSoIfWpdNhG}(see Heller, 2019; Polak, 2019)
\parencites[see][]{heller_how_2019}[][]{polak_philosophy_2019} %
 is that the best sources tend to be atypical from the viewpoint of most philosophers: For example, on the one hand, there are works that popularize science, while on the other hand, there are research articles and even specialized monographs. The book discussed here falls into the last category, and it is devoted to modeling neurons and perceptrons. It was written by a~mathematician from Kraków, Andrzej Bielecki, who is currently working at the AGH University of Science and Technology.\footnote{Andrzej Bielecki received an M.Sc. degree in Physics and Mathematics and a~Ph.D. in Mathematics, D.Sc. (habilitation) in Mathematics from the Jagiellonian University in Kraków. He obtained a~professorship in Computer Science in 2020. His fields of interest includes dynamical systems theory, artificial intelligence, cybernetics, and philosophy of science, and he has written over 120 scientific papers and one textbook.} Readers of \textit{ZFN}, as well as the related \textit{Semina Scientiarum} journal, will probably associate him with the philosophical activities that he has practiced within the context of his scientific activities 
%\label{ref:RNDkz8F1S0BJI}(Bielecki, 2016; 2018).
\parencites*[][]{bielecki_cybernetyczna_2016}[][]{bielecki_epistemologiczne_2018}. %
 Bielecki is an example of a~scientist–philosopher from the Krakow milieu,\footnote{It is worth mentioning that in the book, Bielecki mostly uses examples from research conducted in the Kraków milieu. The use of the cybernetic theory framework could also be interpreted as another sign of the local milieu's influence.} and it is worth noting that he develops his philosophical activities, among other things, through his work on the Committee on Philosophy of Science at the Polish Academy of Arts and Sciences in Kraków.

### 2023-02-06 REV_Polak2/Polak2.tex
Final commit before sending to the editors for corrections

\begin{document}
Beyond Epistemic Concepts of Information: The Case of Ontological Information as Philosophy in Science

Roman Krzanowski, \textit{Ontological information: information in the physical world, series: World Scientific series in information studies}, 13, Hackensack, New Jersey: World Scientific 2022, pp. xii+264.

The concept of information plays and important role in science and philosophy, as well as in everyday life, such that it is now hard to imagine that this concept has been only adopted in the late 1940s. Many scientists find it even harder to believe that the concept of information can involve anything other than communication processes, and this is almost certainly due to Claude Shannon's Theory of Communication (TOC)
%\label{ref:RNDpOqVZWFMX0}(Shannon, 1949)
\parencite[][]{shannon_mathematical_1949} %
 that entered the canon of unquestionable modern scientific knowledge. Unquestionably accepting Shannon's concept of a~measure of information entropy as the definition of information encourages a~scholar to treat TOC as scientific dogma.\footnote{ Shannon himself tried to warn against abusing his theory of communication (Shannon, 1956), though apparently unsuccessfully. He called against using the theory as a~source of hypotheses in other scientific disciplines. However, the opposite has happened—information metaphors have become unquestionable theoretical core of many modern concepts. This fact should not come as a~surprise, because if few people read the original work contenting themselves only with its processed results, it is difficult to suppose that anyone outside a~handful of specialists in the history of computing read Shannon's critical remarks very rarely cited in the literature.} However, studying the original work of Shannon and Weaver 
%\label{ref:RNDBAl2hvYeRw}(1964, p.3),
\parencite*[][p.3]{shannon_mathematical_1964}, %
 we realize that Shannon was primarily interested in communication engineering of digital signals (signal recovery, noise, optimal coding of signal), and the concepts of information and entropy have been borrowed by him from works of physicists like Ludwig Boltzmann, Leo Szilard, and John von Neumann.

@@

Bibliography

Bielecki, A. and Schmittel, M., 2022. The Information Encoded in Structures: Theory and Application to Molecular Cybernetics. \textit{Foundations of Science}, [online] 27(4), pp.1327–1345. https://doi.org/10.1007/s10699-022-09830-8.

Burgin, M. and Mikkilineni, R., 2022. Is Information Physical and Does It Have Mass? \textit{Information}, [online] 13(11), p.540. https://doi.org/10.3390/info13110540.

Heller, M., 2019. How is philosophy in science possible? \textit{Philosophical Problems in Science (Zagadnienia Filozoficzne w~Nauce}), [online] (66), pp.231–249. Available at: {\textless}https://zfn.edu.pl/index.php/zfn/article/view/482{\textgreater} [Accessed 6 October 2021].

Krzanowski, R., 2017. Minimal Information Structural Realism. \textit{Philosophical Problems in Science (Zagadnienia Filozoficzne w~Nauce}), [online] (63), pp.59–75. Available at: {\textless}http://www.zfn.edu.pl/index.php/zfn/article/view/396{\textgreater} [Accessed 16 May 2018].

Krzanowski, R., 2020. Why can information not be defined as being purely epistemic? \textit{Zagadnienia Filozoficzne w~Nauce (Philosophical Problems in Science}), [online] (68), pp.37–62. Available at: {\textless}https://zfn.edu.pl/index.php/zfn/article/view/494{\textgreater}.

Krzanowski, R., 2022. \textit{Ontological Information: Information in the Physical World}. World Scientific series in information studies. [online] Hackensack, New Jersey: World Scientific Publishing Co. https://doi.org/10.1142/12601.

Mścisławski, Ł., 2022. Is information something ontological, or physical or perhaps something else? Some remarks on R. Krzanowski approach to concept of information. \textit{Philosophical Problems in Science (Zagadnienia Filozoficzne w~Nauce}), (73), p.??

Polak, P., 2019. Philosophy in science: A~name with a~long intellectual tradition. \textit{Philosophical Problems in Science (Zagadnienia Filozoficzne w~Nauce}), [online] (66), pp.251–270. Available at: {\textless}https://zfn.edu.pl/index.php/zfn/article/view/472{\textgreater} [Accessed 6 October 2021].

Polak, P. and Trombik, K., 2022. The Kraków School of Philosophy in Science: Profiting from Two Traditions. \textit{Edukacja Filozoficzna}, (2(74)). https://doi.org/10.14394/edufil.2022.0023.

Shannon, C.E., 1949. \textit{The mathematical theory of communication}. Urbana: University of Illinois Press.

Shannon, C.E. and Weaver, W., 1964. \textit{The Mathematical Theory of Communication}. Illini Books. Urbana: University of Illinois Press.

Turek, K., 1978. Filozoficzne aspekty pojęcia informacji. \textit{Philosophical Problems in Science (Zagadnienia Filozoficzne w~Nauce}), (1), pp.32–41.

Turek, K., 1981. Rozważania o~pojęciu struktury. \textit{Philosophical Problems in Science (Zagadnienia Filozoficzne w~Nauce}), (3), pp.73–95.
\end{document}

>>>>

\begin{newrevengenv}{Paweł Polak}
	{Beyond epistemic concepts of information: The case of ontological information as philosophy in science}
	{Beyond epistemic concepts of information\ldots}
	{Beyond epistemic concepts of information: The case of ontological\\information as philosophy in science}
	{Pontifical University of John Paul II in Krakow}
	{Roman Krzanowski, \textit{Ontological information: information in the physical world, series: World Scientific series in information studies}, 13, Hackensack, New Jersey: World Scientific 2022, pp. xii+264.}

%\begin{document}
%Beyond epistemic concepts of information: The case of ontological information as philosophy in science
%
%
%Roman Krzanowski, \textit{Ontological information: information in the physical world, series: World Scientific series in information studies}, 13, Hackensack, New Jersey: World Scientific 2022, pp. xii+264.

\lettrine[loversize=0.13,lines=2,lraise=-0.03,nindent=0em,findent=0.2pt]%
{T}{}he concept of information plays and important role in science and philosophy, as well as in everyday life, such that it is now hard to imagine that this concept has been only adopted in the late 1940s. Many scientists find it even harder to believe that the concept of information can involve anything other than communication processes, and this is almost certainly due to Claude Shannon's Theory of Communication (TOC)
%\label{ref:RNDpOqVZWFMX0}(Shannon, 1949)
\parencite*[][]{shannon_mathematical_1949} %
 that entered the canon of unquestionable modern scientific knowledge. Unquestionably accepting Shannon's concept of a~measure of information entropy as the definition of information encourages a~scholar to treat TOC as scientific dogma.\footnote{ Shannon himself tried to warn against abusing his theory of communication (Shannon, 1956), though apparently unsuccessfully. He called against using the theory as a~source of hypotheses in other scientific disciplines. However, the opposite has happened—information metaphors have become unquestionable theoretical core of many modern concepts. This fact should not come as a~surprise, because if few people read the original work contenting themselves only with its processed results, it is difficult to suppose that anyone outside a~handful of specialists in the history of computing read Shannon's critical remarks very rarely cited in the literature.} However, studying the original work of Shannon and Weaver 
%\label{ref:RNDBAl2hvYeRw}(1964, p.3),
\parencite*[][p.3]{shannon_mathematical_1964}, %
 we realize that Shannon was primarily interested in communication engineering of digital signals (signal recovery, noise, optimal coding of signal), and the concepts of information and entropy have been borrowed by him from works of physicists like Ludwig Boltzmann, Leo Szilard, and John von Neumann.

@@

\vspace{15mm}%
{\subsubsectit{\hfill Abstract}}\\
{[to be inserted afterr the proofreading]

[to set pages range in rereference (Mścisławski, 2022) during typesetting ?]}\par%
\vspace{2mm}%
{\subsubsectit{\hfill Keywords}}\\
{ontological information, Mark Burgin}%

\end{newrevengenv}
